\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-11-09 response2.tex
Pffft

\tba

>>>>

\begin{response}
  We no longer talk about ``interiors of faces''.  Faces are already defined as the connected components one gets after cutting a surface along all the edges of the (embedded) graph, so faces are already open sets.  In this particular instance we now write ``the interior of each edge in $E(G)\setminus E(G_0)$ is contained in some face (possibly the outer face) of $G_0$.''
\end{response}
